Figures

### 2020-02-13 manuscript/figures.Rmd
reorder figs

@@

@@

```{r lgnemanual-vs-bathy-depth, fig.cap="Comparison between reported max depth and max depth calculated from bathymetry surfaces.", warning=FALSE, echo = FALSE, eval=TRUE}
knitr::include_graphics("../figures/lgnemanual-vs-bathy-depth-1.pdf")
```

@@

![Slope diagram caption](../figures/slope_diagram.pdf){width=100%}

>>>>

![Diagram showing the assumption of most lake depth models that the nearshore slope is extends into the lake and that all lakes have a common relationship between nearshore and in-lake slope. ](../figures/slope_diagram.pdf){width=90%}

@@

```{r lgnemanual-vs-bathy-depth, fig.cap="Comparison between reported max depth and max depth calculated from bathymetry surfaces.", warning=FALSE, echo = FALSE, eval=TRUE}
# see 00_qa.Rmd
knitr::include_graphics("../figures/lgnemanual-vs-bathy-depth-1.pdf")
```

@@

@@
